Thesis Draft

### 2017-09-28 thesis/draft.Rmd
fixed for LaTeX

Focusing on the date 04/07/2014, which has 3 hours of missing data:
```{r}
fit_dat_plot <- data.frame(Date_Time = dfa2$Date_Time,
                           fit_ = dfa2$`Southern Cross Station`) %>%
                  filter(Date_Time < "2014-07-06 00:00:00",
                         Date_Time > "2014-07-04 12:00:00") %>%
                        .$fit_

>>>>

Focusing on the date 04/07/2014, which has 3 hours of missing data:

```{r}
fit_dat_plot <- data.frame(Date_Time = dfa2$Date_Time,
                           fit_ = dfa2$`Southern Cross Station`) %>%
                  filter(Date_Time < "2014-07-06 00:00:00",
                         Date_Time > "2014-07-04 12:00:00") %>%
                        .$fit_
